\documentclass[letterpaper, 11pt]{article}

% Import packages.
\usepackage{anyfontsize}
\usepackage{array}
\usepackage[english]{babel}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
% letter paper is 21.59cm, margins are 1in=2.54cm on each side so the content is 16.51cm wide
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{titlesec} 
\usepackage[usenames,dvipsnames]{xcolor}

% Configure imported packages.
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
% Customize sections.
\titleformat{\section}{\normalsize\scshape\raggedright}{}{0em}{}[\titlerule]
% spacing around sections
\titlespacing{\section}{0pt}{1em}{3pt} 
% Table column alignment options.
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}  
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
% Remove spacing before itemize
\setlist{nolistsep}
% itemize bullet size
\renewcommand\labelitemi{\scriptsize$\bullet$}

\begin{document}

%% NAME
\begin{center}
{\large Thomas Propson} \\[5pt]
\href{mailto:tpropson@mit.edu}{tpropson@mit.edu} $\vert$
\href{https://thomaspropson.com}{thomaspropson.com}
\end{center}


\flushleft

%% EDUCATION
\section{Education}
\begin{tabular}{@{} L{12cm} @{} R{4.51cm} @{}}
  \textbf{Massachusetts Institute of Technology} & 2021--2026\\
  Ph.D. Electrical Engineering\\
\end{tabular}
\begin{tabular}{@{} L{12cm} @{} R{4.51cm} @{}}
  \textbf{The University of Chicago} & 2017--2021\\
  B.A. Physics (summa cum laude), Minor Computer Science\\
\end{tabular}

%% HONORS AND AWARDS
\section{Honors and Awards}
\begin{tabular}{@{} L{14.5cm} @{} R{2.01cm} @{}}
  National Science Foundation Graduate Research Fellowship & 2021\\
  Jacobs Presidential Fellowship, MIT EECS & 2021\\
  Grainger Scholarship, UChicago Physics, full-tuition senior year & 2020\\
  Barry Goldwater Scholarship & 2020\\
  Enrico Fermi Scholar, UChicago PSD, major GPA in top 5\% from past 5 years & 2020\\
  Summer Research Fellowship, UChicago & 2019\\
  Liew Family College Research Fellowship, UChicago & 2018\\
  Jeff Metcalf Research Fellowship, UChicago & 2018 \\
  University Scholarship, UChicago & 2017--2021\\
\end{tabular}

%% PUBLICATIONS
\section{Publications}
\begin{enumerate}
\item A. J. Menssen, A. Hermans, I. Christen, \textbf{T. Propson}, C. Li, A. Leenheer,
  M. Zimmermann, M. Dong, H. Larocque, H. Raniwala, G. Gilbert, M. Eichenfield, D. R. Englund.
  Scalable Photonic Integrated Circuits for Programmable Control of Atomic Systems.
  [\href{https://arxiv.org/abs/2210.03100}{arxiv:2210.03100}].
\item I. Christen, M. Sutula, \textbf{T. Propson}, H. Sattari, G. Choong, C. Panuski, A. Melville, J. Mallek,
  S. Hamilton, P. B. Dixon, A. J. Menssen, D. Braje, A. H. Ghadimi, D. R. Englund.
  An Integrated Photonic Engine for Programmable Atomic Control.
  [\href{https://arxiv.org/abs/2208.06732}{arxiv:2208.06732}].
\item S. Narayanan, \textbf{T. Propson}, M. Bongarti, J. Hueckelheim, P. Hovland.
  Reducing Memory Requirements of Quantum Optimal Control.
  [\href{https://arxiv.org/abs/2203.12717}{arxiv:2203.12717}].
\item \textbf{T. Propson}, B. E. Jackson, Z. Manchester, J. Koch, D. I. Schuster. Robust Quantum
  Optimal Control with Trajectory Optimization.
  \href{https://journals.aps.org/prapplied/abstract/10.1103/PhysRevApplied.17.014036}{
    Phys. Rev. Applied 17(1), 014036} (2022).
  [\href{https://arxiv.org/abs/2103.15716}{arxiv:2103.15716}].
\item Y. Ding, P. Gokhale, S. F. Lin, R. Rines, \textbf{T. Propson}, F. T. Chong.
  Systematic Crosstalk Mitigation for Superconducting Qubits via Frequency-Aware Compilation.
  \href{https://ieeexplore.ieee.org/document/9251858}{Proceedings of the 53rd Annual
  IEEE/ACM International Symposium on Microarchitecture, 201-214} (2020).
       [\href{https://arxiv.org/abs/2008.09503}{arxiv:2008.09503}].
\item P. Gokhale, Y. Ding, \textbf{T. Propson}, C. Winkler, N. Leung, Y. Shi,
  D. I. Schuster, H. Hoffmann, F. T. Chong.
  Partial Compilation of Variational Algorithms for Noisy Intermediate-Scale Quantum Machines.
  \href{https://doi.org/10.1145/3352460.3358313}{Proceedings of the 52nd Annual
    IEEE/ACM International Symposium on Microarchitecture, 266-278} (2019).
       [\href{https://arxiv.org/abs/1909.07522}{arxiv:1909.07522}].
\end{enumerate}

%% PATENTS
\section{Patents}
\begin{enumerate}
  \item P. Gokhale, Y. Ding, \textbf{T. Propson}, F. T. Chong, "System and Method
    for Partial Compilation of Variational Algorithms in Quantum Computers." Intl. App. No. PCT/US2020/049932
\end{enumerate}

%% TALKS
\section{Contributed Talks}
Systematic Crosstalk Mitigation for Superconducting Qubits via Frequency-Aware Compilation\\
\begin{itemize}
  \item MICRO 53 Conference (virtual), Athens, Greece, 2020\\
\end{itemize}
Partial Compilation of Variational Algorithms for Noisy Intermediate-Scale Quantum Machines\\
\begin{itemize}
\item MICRO 52 Conference, Columbus, OH, 2019\\
\end{itemize}
Commercial Outlook for Quantum Computing\\
\begin{itemize}
\item The University of Chicago Booth School of Business, Chicago, IL, 2019\\
\end{itemize}

%% POSTERS
\section{Contributed Posters}
Benchmarking Hyperparameter Optimization Algorithms on Deep Neural Networks\\
\begin{itemize}
\item The University of Chicago Undergraduate Research Symposium, Chicago, IL, 2018\\
\item Argonne National Laboratory Summer Student Symposium, Lemont, IL, 2018\\
\end{itemize}

%% SERVICE
\section{Outreach}
\begin{tabular}{@{} L{12cm} @{} R{4.51cm} @{}}
  \textbf{The University of Chicago Department of Physics} & 2020--2021\\
\end{tabular}
\begin{itemize}
\item Organize a pre-freshman, summer, physics program for first-generation and limited-income
  students
\end{itemize}

\begin{tabular}{@{} L{12cm} @{} R{4.51cm} @{}}
  \textbf{Uncommon Hacks} & 2018--2021\\
\end{tabular}
\begin{itemize}
\item Organize an annual MLH endorsed hackathon to provide a platform for 300+
  students to collaborate with peers, learn technical skills,
  and develop relationships with employers
\item Lead a 10-person team of designers and software developers
  to build websites that reach 1000+ users
\end{itemize}

\begin{tabular}{@{} L{12cm} @{} R{4.51cm} @{}}
  \textbf{Strive Learning} & 2018\\
\end{tabular}
\begin{itemize}
\item Met weekly with students from limited-income households in the Chicago Public Schools
  to assist with coursework, college applications, and connecting
  students to extracurricular activities
\end{itemize}

%% TEACHING
\section{Teaching}
\textbf{The University of Chicago}
\begin{itemize}
  \item Grader, Winter 2020, CMSC 23300 Networks and Distributed Systems
\end{itemize}

%% WORK EXPERIENCE
\section{Work Experience}
\begin{tabular}{@{} L{12cm} @{} R{4.51cm} @{}}
  \textbf{PanorArt Inc.} & 2018 \\
  Full-Stack Web Developer\\
\end{tabular}
\begin{itemize}
\item Angular, Node.js, HTTP, relational and non-relational databases, search engine optimization
\end{itemize}

\end{document}
